\begin{frame}[allowframebreaks]
    \frametitle{Comments}
    
    \begin{enumerate}
        \item Lack of rigorous mathematical proof \\[2em]
        
        Some propositions and lemmas are concluded without a proper proof, 
        and some are even contradicting one another. 

        For example, in proposition 4, both offering best contract yields equilibria for 
        all $f\in(0,k)$, but in the elaborative proof of proposition 7, he concludes that 
        even both in the optimal contract level, the foreign central bank extracts all deposit, 
        identical to justifying that $f=k$, which contradicts to his previous claim of multiple equilibria.

        \item The roll of CBDC in this paper\\[2em]
        
        It is unclear how CBDC deposit differs from other risk-free assets such as 
        US treasury bond. 

        Accessibility might be something the author used to justify this possibility, but as agents don't see benefits from 
        substituting a potential means of payment for another, this explanation is not convincing. 

        \framebreak 

        \item Connection with fundamentals \\[2em]
        
        As with typical Diamond and Dybvig structure, the run happens purely from a sunspot shock. 
        If fundamentals are not considers, any country turns out to be vulnerable after dollar is digitalized. 

        Conditions such as high inflation rate, described in Calvo (1922), exacerbated currency substitution, 
        which are more likely to set the domestic financial system on crisis.
        
 
    \end{enumerate}

\end{frame}

\begin{frame}
    \frametitle{Extensions / Motivations for ABM}

    \begin{enumerate}[<+->]
        \item Consider the roll of CBDC as a mean of payment
        \begin{itemize}[<.->]
            \item Endogenously emerge as a MoP
            \item Becoming MoP, then causes run? 
            \item Or first run, then ended up as a MoP? 
        \end{itemize}
        \item Understand how such disintermediation damages the economy, 
        and the best measure government could conduct to cease the crisis.
        \item The role of exchange rate
        \begin{itemize}[<.->]
            \item Will purchasing power imparity emerge endogenously? (No story yet)
            \item Purchasing power imparity cause direct demand on foreign currency ($\because$ easy access)
            \item Holding F-CBDC is optimal
            \item Further cause devaluation on domestic currency, PP drop further
        \end{itemize}
        
    \end{enumerate}

    

\end{frame}